---
title: "ROracle : R and Oracle database"
author: "Kumar Halake"
date: "12 December 2017"
output: html_document
---

Email : [halake.kumar22@gmail.com](halake.kumar22@gmail.com)

### ------------------------------------------------------------------------------------------------------------------
* The main purpose of this workout is just to know how `ROracle` package is useful to connect, query, fetch table, etc from Oracle RDBMS

* The ODI Cricket dataset contains Country,Player and his runs and score rate with match date.
 Data pertaining to all ODI's played from **January 1971** to **September 2011** are in this dataset. So obviously  runs and score rates vary if a player is played after **September 2011** 

* The `dplyr` and `ggplot2` packages are aslo used wherever necessary


```{r,include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE,comment = "",fig.align = 'center')

library(ROracle)
library(DBI)
library(ggplot2)
library(dplyr)
library(png)
library(grid)
```

### ------------------------------------------------------------------------------------------------------------------

### Creating the Connection
```{r}
driver<- Oracle()
#driver <- dbDriver("Oracle")

 host <- "localhost"
 port <- 1521
 service <- "Orcl1"
 drv <- dbDriver("Oracle")

 connect.string <- paste(

 "(DESCRIPTION=",

 "(ADDRESS=(PROTOCOL=tcp)(HOST=", host, ")(PORT=", port, "))",

 "(CONNECT_DATA=(SERVICE_NAME=", service, ")))", sep = "")

 connection <- dbConnect(drv, username = "system", password = "Oracle_1", dbname = connect.string)
 
 
 #connection <- dbConnect(drv = driver, username = "system", password = "Oracle_1")
```

### ------------------------------------------------------------------------------------------------------------------

### Storing and removing some data in database
```{r}
# Store first 10 rows of iris in Oracle database as an 'iris' table
dbWriteTable(connection, 'IRIS', iris[sample(nrow(iris),10,replace = T),], overwrite = TRUE, row.names = FALSE,col.names = FALSE)

# IMP : The Iris data has some columns of type double. When one see the same data in SQL Developer(What I used), the data totally looks different (eg 3.0 in r is 2.9999999 in SQL) So, manipulating may throw error sometimes in R

# If some queries are sending to same table from SQL developer and ROracle connection, sometimes we get error in R, so better to use one at time
```

```{sql,connection = connection}
 SELECT DISTINCT "Species" FROM IRIS
```

```{sql,connection = connection}
 SELECT * FROM IRIS
```

```{r}
dbExistsTable(connection,'IRIS')  # Check whether iris table exists? -> TRUE / FALSE

dbReadTable(connection, "IRIS") %>% head(n = 10) # Read first 5 rows of iris table in database

dbRemoveTable(connection,'IRIS')  # Remove the table iris,runs only when no query is running like rs

dbExistsTable(connection,'IRIS')  # Whether iris exists yet?
```

### ------------------------------------------------------------------------------------------------------------------

### Importing the ODI data frame from Oracle to R.

Sometimes for any type of explorations (eg:Graphical), one may need to read the entire table from database. It can be achieved by `dbReadTable`. The table imported is in *Dataframe* format. The Field types are accordingly adjusted.

In oracle database the *ODI* dataset already exist.

```{r}
ODI = dbReadTable(connection, "ODI")
glimpse(ODI)
head(ODI,n=3)
object.size(ODI)
class(ODI)
```

```{sql,connection = connection}
SELECT TO_CHAR(MIN(MATCHDATE),'DDth-Month-YYYY') Begin,TO_CHAR(Max(MATCHDATE),'DDth-Month-YYYY') "End" FROM ODI
```

### ------------------------------------------------------------------------------------------------------------------

### Some Commands from `ROracle` package

```{r}
names(dbGetInfo(connection))
names(dbGetInfo(driver))
dbDataType(dbObj = connection,obj = 1:10) # (Dtatype of R object interms of SQL object)
dbDataType(dbObj = connection,obj = iris)
dbDataType(dbObj = connection,obj = "what is it?")
#dbDataType(dbObj = connection,obj = odi)
dbDataType(ANSI(), 1:5)
dbDataType(ANSI(), TRUE)
dbDataType(ANSI(), Sys.Date())
dbDataType(ANSI(), list(raw(10), raw(20)))
dbDataType(ANSI(), I(3))
dbExistsTable(connection,"ODI") # Chech whether table exixts in 
dbExistsTable(connection,"Some_datatable")
dbListTables(connection) %>% tail(20) # Checking the list of Tables avaiable in Oracle DB.
dbListFields(connection,'ODI') # Colnames
dbListResults(connection) # history
dbGetException(connection) # last error in the connection

# dbGetInfo(connection)  # Connection details
# dbGetInfo(driver)  #
# dbListConnections(drv = driver) # Get host,port,SID in driver
# dbExecute  # -  number of rows affected by statements
# dbSendQuery
# dbGetQuery =  dbSendQuery() + dbFetch() + dbClearResult

# dbGetRowCount #  Number of rows fetched so far

# dbRemoveTable()
# dbSendStatement()  #  is for DML : UPDATE, DELETE, INSERT INTO, DROP TABLE, ...
# dbGetRowsAffected # - This method returns the number of rows that were added, deleted, or updated by a data manipulation statement

# dbWriteTable #  read data in Oracle database
# dbReadTable
# dbRemoveTable
# fetch  # fetching certain number of instances
# dbFetch
# dbHasCompleted #  This method returns if the operation has completed. A SELECT query is completed if all rows have been fetched. A data manipulation statement is always completed.

# dbIsValid # Is this DBMS object still valid?

# dbBegin # savepoint
# dbBreak
# dbCommit
# dbRollback
# dbWithTransaction() 
# sqlAppendTable #  Insert rows into a tabl
# sqlCreateTable #  Create a simple table
# sqlData #  Convert a data frame into form suitable for upload to an SQL database
# transactions # Begin/commit/rollback SQL transactions
# dbDisconnect()  # Disconnect R from Oracle database
```


Sometimes data may be having larger in size,importing a large volume of data in R is not recommended.
So just querrying by letting it in database itself is a better choice.

### ------------------------------------------------------------------------------------------------------------------

### SQL Queries

* *Note that the reslut of any SQL query may not be completely displayed in html outpot*

#### number of matches
```{sql,connection = connection}
SELECT COUNT(*) FROM ODI /* number of matches */
```

#### Countrywise average runs
```{sql,connection = connection}
SELECT COUNTRY, AVG(RUNS) as avg_runs FROM ODI GROUP BY COUNTRY
```

#### Merging fields
```{sql connection=connection}
SELECT COUNTRY||AVG(RUNS) as Country_avg_Runs FROM ODI GROUP BY COUNTRY
```

```{sql connection=connection}
SELECT GROUND||'-'||cOUNT(GROUND) FROM ODI GROUP BY GROUND
```

```{sql connection=connection}
SELECT GROUND||'-'||cOUNT(GROUND) AS "GROUNDWISE COUNT" FROM ODI GROUP BY GROUND ORDER BY COUNT(GROUND) DESC
```

```{sql connection=connection}
SELECT COUNTRY ||' vs '|| VERSUS ||' at '|| GROUND ||' - ' || COUNT(GROUND) AS "Country-Versus-Ground-n" FROM ODI GROUP BY COUNTRY,VERSUS,GROUND ORDER BY COUNT(GROUND) DESC
```

### ------------------------------------------------------------------------------------------------------------------

#### Data related to India
```{sql connection=connection}
SELECT*FROM ODI WHERE COUNTRY = 'India' /*  Only first 10 rows are displayed */
```

#### Maximum runs by India versus all countries it played and the corresponding player

```{sql connection=connection}
SELECT COUNTRY,VERSUS,PLAYER,RUNS FROM ODI WHERE RUNS IN 
(SELECT MAX(RUNS) AS RUNS FROM ODI WHERE COUNTRY='India' GROUP BY VERSUS) AND COUNTRY = 'India' ORDER BY RUNS DESC
```

*  Is it correct output ? Check how many opponent countries are there for India. They are 20 not 132

```{sql connection=connection}
SELECT COUNT(*) FROM (SELECT COUNTRY,VERSUS,PLAYER,RUNS FROM ODI WHERE RUNS IN 
(SELECT MAX(RUNS) AS RUNS FROM ODI WHERE COUNTRY='India' GROUP BY VERSUS) AND COUNTRY = 'India' ORDER BY RUNS DESC)
```

```{sql, connection = connection}
SELECT COUNT(DISTINCT VERSUS) FROM ODI WHERE COUNTRY = 'India'
```

```{sql connection=connection}
SELECT o.COUNTRY, o.VERSUS,o.MATCHDATE,o.PLAYER,o.RUNS FROM ODI o JOIN 
(SELECT COUNTRY,VERSUS, MAX(RUNS) AS highest_runs FROM ODI WHERE COUNTRY = 'India' GROUP BY COUNTRY,VERSUS) d 
ON o.COUNTRY=d.COUNTRY AND o.VERSUS = d.VERSUS AND o.RUNS = d.highest_runs ORDER BY o.RUNS DESC
```

* 21 rows because same highest runs in 1999 and 2005 by **Sourav C Ganguly** and **Mahendra S Dhoni** respectively against **Sri Lanka**

<!-- ```{sql connection=connection} -->
<!-- SELECT o.COUNTRY, o.VERSUS, MAX(o.RUNS) AS highest_runs FROM ODI o INNER JOIN ODI d ON o.highest_runs = d.RUNS, o.COUNTRY = d.COUNTRY, o.VERSUS = d.VERSUS WHERE o.COUNTRY = 'India' GROUP BY o.COUNTRY, o.VERSUS ORDER BY O.highest_runs DESC -->
<!-- /* The aggregation function must come in getting joined table, not in joining table -->
<!-- ``` -->

### ------------------------------------------------------------------------------------------------------------------

#### Maximum runs of each player and the country he belongs to
```{sql connection=connection}
SELECT COUNTRY,PLAYER,MAX(RUNS) AS RUNS FROM ODI GROUP BY COUNTRY,PLAYER
```

#### Country ever having more runs than max runs by India  
```{sql connection=connection}
SELECT COUNTRY,RUNS FROM ODI WHERE RUNS > (SELECT MAX(RUNS) AS RUNS FROM ODI WHERE COUNTRY = 'India' GROUP BY COUNTRY) /* No country */
```

* The same result is achieved by JOIN also. Joins are recommended over nested Subqueries like above

```{sql connection=connection}
SELECT o.COUNTRY,O.RUNS FROM ODI o JOIN 
(SELECT COUNTRY,MAX(RUNS) AS max_run FROM ODI WHERE COUNTRY = 'India' GROUP BY COUNTRY) b
ON o.COUNTRY = b.COUNTRY AND o.RUNS >b.max_run
/* No country, by putting >=, will get India only */
```

### ------------------------------------------------------------------------------------------------------------------

####  Score rate variation for different Countries
```{sql connection=connection}
SELECT COUNTRY, stddev(SCORERATE) sd FROM ODI GROUP BY COUNTRY ORDER BY sd 
```

### ------------------------------------------------------------------------------------------------------------------

### R QUERIES

#### Fetch and save in R 

Here, the previous SQL query output is saved in R as dataframe, so one can use to to explore in different ways like graphs.

```{r}
df <- dbGetQuery(connection,"SELECT DISTINCT TO_CHAR(MATCHDATE,'YYYY') FROM ODI")
class(df)       # It is dataframe
typeof(df)
colnames(df)  # default column name
class(df$`TO_CHAR(MATCHDATE,'YYYY')`)  # It is character
head(df)
object.size(df)
```

### ------------------------------------------------------------------------------------------------------------------

#### Monthwise number of matches
```{r,fig.height=5}
  dbGetQuery(connection,statement = "SELECT TO_CHAR(MATCHDATE,'mm') MONTH FROM ODI") %>%
  ggplot() +
  geom_bar(aes(x = as.numeric(MONTH)),stat = "count",fill = rainbow(12),alpha = 0.6) +
  theme(panel.grid = element_blank(),panel.background = element_blank(),
        axis.ticks = element_blank(),axis.text.x = element_text(angle = 90))+
  scale_x_discrete(limits = 1:12, labels = month.name) +
  labs(y = "Number of matches", x = "Month", title = "Matches in each month")+
  theme(plot.title = element_text(face = "bold",color = "gray83",hjust = 0.5,size = 12))
```

### ------------------------------------------------------------------------------------------------------------------

#### Number of matches per Year and month
```{r,fig.height=7,fig.width=12}
dbGetQuery(connection,"SELECT TO_CHAR(MATCHDATE,'YYYY') YEAR, TO_CHAR(MATCHDATE,'MM') MONTH FROM ODI") %>%
  ggplot() +
  geom_bar(aes(x = YEAR,fill = as.factor(MONTH)), stat = "count",color = "purple",alpha = 0.9,size = 0.04) +
  theme(axis.text.x.top = element_text(angle = 90),
        panel.background = element_rect(fill = "gray80"),
        plot.background = element_rect(fill = "gray80"),
        axis.ticks = element_blank(),
        legend.background = element_rect(fill = "gray83"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(colour = "gray40",linetype = 3,lineend = 'butt')) +
  scale_y_continuous(expand = c(0.0,0),breaks = seq(0,3500,by = 250)) +
  scale_fill_brewer(name = 'Months',labels = month.name,palette = "Set3",direction = 1) +
  coord_flip()
```


* Normally in any given year, most number of matches were played in first quarter
* 1971 and 1972 are the beginning years where match happened only in a single monthyear
* From the year 1991 we see some seasonal pattern interms of yerly number of matches.
 (the number of matches are relatively less in 1991, but in next consecutive 3 years it increased. Again number reduced in 1995 and tremendous increase in next 3 years)

### ------------------------------------------------------------------------------------------------------------------

#### India's highest runs against different opponents

```{r,fig.height=5,fig.width=5}
dbGetQuery(connection,
"SELECT o.COUNTRY, o.VERSUS,o.MATCHDATE,o.PLAYER,o.RUNS FROM ODI o JOIN 
(SELECT COUNTRY,VERSUS, MAX(RUNS) AS highest_runs FROM ODI WHERE COUNTRY = 'India' GROUP BY COUNTRY,VERSUS) d
ON o.COUNTRY=d.COUNTRY AND o.VERSUS = d.VERSUS AND o.RUNS = d.highest_runs ORDER BY o.RUNS DESC") %>% 
  group_by(VERSUS) %>% summarise(RUNS = mean(RUNS)) %>% # Srilanka is twice,we need unique so
  ggplot() + geom_bar(aes(x = reorder(VERSUS,RUNS), y = RUNS),stat = "identity",fill = "springgreen") +
  labs(x="Opponent", y ="Maximum Runs",title = "Maximum Runs of India") + coord_flip() +
  theme_bw()
```

### ------------------------------------------------------------------------------------------------------------------

#### Top number of centuries

```{sql,connection = connection}
SELECT PLAYER,COUNT(PLAYER) CENTURY FROM ODI WHERE RUNS >= 100 GROUP BY PLAYER ORDER BY CENTURY DESC FETCH NEXT 21 ROWS ONLY
```

```{r,fig.height=5.5,fig.width=12}
img <- readPNG("sachin-transpa-2.png") 
g <- rasterGrob(img, interpolate=TRUE) 

  dbGetQuery(connection,
             statement = "SELECT PLAYER,COUNT(PLAYER) CENTURY FROM ODI WHERE RUNS >= 100 GROUP BY PLAYER ORDER BY CENTURY DESC FETCH NEXT 21 ROWS ONLY") %>%
  ggplot(aes(x = reorder(PLAYER,desc(CENTURY)),y = CENTURY)) +
    annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) + 
    geom_bar(stat = "identity",fill = rainbow(21),alpha = 0.6) +
    geom_text(aes(label = CENTURY,size =CENTURY),show.legend = FALSE,vjust = - 0.09,color = rainbow(21)) +
    theme(panel.grid = element_blank(),
          panel.background = element_rect(fill = "gray80"),
          plot.background = element_rect(fill = "gray80"),
          axis.ticks = element_blank(),axis.text.x = element_text(angle = 90,hjust = 1.0)) +
    scale_y_continuous(limits = c(0,52),labels = NULL) + 
    labs(y = "", x = "Batsman", title = "Top number of centuries") +
    theme(plot.title = element_text(face = "bold",color = "white",hjust = 0.5,size = 12))
```

### ------------------------------------------------------------------------------------------------------------------

#### Some functions `dbSendQuery`,`dbGetStatement`,`dbGetRowsAffected`,`fetch`

```{r}
q = "SELECT COUNTRY,VERSUS,PLAYER,RUNS FROM ODI WHERE COUNTRY = 'India'"

rs = dbSendQuery(connection,q)
rs
dbGetStatement(rs)

dbGetRowsAffected(rs)

dbColumnInfo(rs)

dbHasCompleted(rs)

fetched1 = fetch(rs,25) # Once first n instances are fetched, they wont be fetched again,In the next fetch, fetching start from next instance only. If no mention of n, all instances are fetched 

fetched2 = fetch(rs) # If dont give n, it will fetch remaining instances from DBIresult as a subset : fetch2

dbHasCompleted(rs)

fetched1 # dont forget, It is dataframe

fetched = rbind(fetched1,fetched2) # At the begining itself would have used fetched = fetch(rs)

dbGetRowCount(rs)  # s the number of rows fetched so far.

dbClearResult(rs)  # after setting dbClearResult(rs); print(rs)  produces an error, as it is cleared
```

 Fetching is helpful when there is limitation on fetching instances from database

### ------------------------------------------------------------------------------------------------------------------

#### Top 20 Indian player's interms of average score rate
```{sql connection=connection}
SELECT COUNTRY,PLAYER,AVG(SCORERATE) AS AVG_SCORE_RATE FROM ODI WHERE COUNTRY = 'India' GROUP BY COUNTRY,PLAYER  ORDER BY AVG_SCORE_RATE DESC FETCH NEXT 20 ROWS ONLY
/* FETCH FIRST 20 ROWS ONLY */
```

```{r,fig.height=5}
q = "SELECT COUNTRY,PLAYER,AVG(SCORERATE) AS AVG_SCORE_RATE FROM ODI WHERE COUNTRY = 'India' GROUP BY COUNTRY,PLAYER  ORDER BY AVG_SCORE_RATE DESC"
rs = dbSendQuery(connection,q)
fetch(rs,20) %>% ggplot() + 
  geom_bar(aes(x = reorder(PLAYER,AVG_SCORE_RATE),y = AVG_SCORE_RATE),
           stat="identity",fill = rainbow(20),width = .6,alpha = 0.6) +
  labs(x = "Top 20 Players",y = "Average Score rate",title ="") + coord_flip() + theme_light()
dbClearResult(rs)
```

### ------------------------------------------------------------------------------------------------------------------

#### Top Players interms of average score rate for all countries

There are some players who played once or twice and their score rate would be either very high or very low.
So we consider a player who played more than 5 ODI's (This choice is subjective, so please no question - *WHY 5?*)

```{sql,connection = connection}
 SELECT COUNT(*) FROM (SELECT COUNTRY,PLAYER, AVG(SCORERATE) AVG_SCORE_RATE,COUNT(*) MATCHES FROM ODI GROUP BY COUNTRY,PLAYER)
```

```{sql,connection = connection}
SELECT COUNT(*) FROM (SELECT COUNTRY,PLAYER, AVG(SCORERATE) AVG_SCORE_RATE,COUNT(*) MATCHES FROM ODI HAVING COUNT(*) > 5 GROUP BY COUNTRY,PLAYER)
```

```{r,echo=FALSE}
cat(c("Almost",1937-1174,"Players played 5 or less matches"))
```

```{r,fig.width=12,fig.height=20}
q = "SELECT COUNTRY,PLAYER, AVG(SCORERATE) AVG_SCORE_RATE,COUNT(*) MATCHES FROM ODI HAVING COUNT(*) > 5 GROUP BY COUNTRY,PLAYER"
rs = dbSendQuery(connection,q)
fetched = fetch(rs) #dbFetch is also useful
country_list = split(x = fetched,f = fetched$COUNTRY)

top_20_each <- lapply(X = country_list, FUN = function(x) top_n(x,20))

g = list()
j = 1
while(j <= length(top_20_each)){
  for(i in names(top_20_each)){
    g[[j]] = ggplot(top_20_each[[i]],aes(x = reorder(PLAYER,AVG_SCORE_RATE),y = AVG_SCORE_RATE)) + 
      geom_bar(stat = "identity",width = 0.25,fill = "white",color = "steelblue1") +
      scale_y_continuous(breaks = seq(0,120,by = 40),limits = c(0,120),labels = seq(0,120,by = 40)) +
      labs(x = "",y = "",title = i) +
      theme_minimal() +
      theme(plot.title = element_text(size = 8),axis.title = element_text(size = 7)) +
      coord_flip()
    j = j+1
  }
}

do.call(gridExtra::grid.arrange,c(g,ncol = 3))
dbClearResult(rs)
```

### ------------------------------------------------------------------------------------------------------------------

#### Correlation between Runs and scorerate for England Players
```{r,fig.height=6.8}
q = "SELECT PLAYER,RUNS,SCORERATE FROM ODI WHERE COUNTRY = 'England'"

dbGetQuery(connection,statement = q) %>%
  group_by(PLAYER) %>%
  summarise(correlation = cor(RUNS,SCORERATE)) %>%
  filter(abs(correlation) > 0.8) %>%
  ggplot(aes(x = reorder(PLAYER,correlation),y = correlation)) +
  geom_dotplot(binaxis='y', stackdir='center',
           stat = "identity",radius = 0.2, fill = rainbow(42)) +
  labs(x = "Player",title = "Correlation between Score rate and Runs",subtitle = "[For England Only]") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.background = element_rect(fill = "gray90")) +
  coord_flip()

# dbGetQuery(connection,statement = q) %>% 
#   group_by(PLAYER) %>% 
#   summarise(correlation = cor(RUNS,SCORERATE)) %>% 
#   filter(abs(correlation) > 0.8) %>% 
#   ggplot(aes(x = reorder(PLAYER,correlation),y = correlation)) +
#   geom_point(size = 5, color = rainbow(42),pch =19) +
#   labs(x = "Player",title = "Correlation between Score rate and Runs") +
#   theme(panel.grid = element_blank(),plot.background = element_rect(fill = "gray90")) +
#   coord_flip()
```


 Here we have noticed two outliers, *Alex Jeremy Tudor* and *Geoffrey W Humpage*, whose correlation is perfect -ve.

### ------------------------------------------------------------------------------------------------------------------

```{r}
q = "SELECT*FROM ODI WHERE COUNTRY = 'England' AND PLAYER IN ('Alex Jeremy Tudor','Geoffrey W Humpage')"
rs = dbSendQuery(connection,q)
outliers = dbFetch(res = rs, n = -1)
outliers= mutate(outliers,balls_faced = SCORERATE*RUNS/100)
outliers
dbClearResult(rs)
```

This is because both the players played only in 1981 and 2002 and not even played for a complete over.

#### The rare players

 Number of players played only once (In time period from 1971 to 2011)
```{r}
q = "SELECT COUNTRY,PLAYER,COUNT(PLAYER) AS MATCHES  FROM ODI GROUP BY COUNTRY,PLAYER HAVING COUNT(PLAYER) = 1"
rs = dbSendQuery(connection,q)
rare = dbFetch(res = rs, n = -1)
rare %>% group_by(COUNTRY) %>% summarise(rare_players = sum(MATCHES)) %>% arrange(desc(rare_players))
dbClearResult(rs)
```

Totally 225 players in ODI from 1971 to 2011 played once.

### ------------------------------------------------------------------------------------------------------------------

#### Long time career in ODI

Note that this is different than the number of ODI's played


```{r,fig.width=10,fig.height=6,fig.align='center'}
q = 'SELECT PLAYER ,BEGIN,"END",MED,"END" - BEGIN AS DAYS,("END" - BEGIN)/365 AS YEAR FROM
(SELECT PLAYER,MIN(MATCHDATE) BEGIN,MAX(MATCHDATE) "END",MEDIAN(MATCHDATE) MED FROM ODI GROUP BY PLAYER) ORDER BY YEAR DESC FETCH NEXT 20 ROWS ONLY'
# aes(x = reorder(PLAYER,DIFF),y=DIFF)
rs = dbSendQuery(connection,q)
dbFetch(rs,n= -1) %>% ggplot() + 
  geom_errorbar(aes(x = reorder(PLAYER,YEAR),ymin=BEGIN,ymax = END),stat="identity",size = 7.5,color = rainbow(20))+
  geom_text(aes(x = reorder(PLAYER,YEAR),y=MED,label = paste(PLAYER,',',round(YEAR,2),'years'),size = 7)) +
  theme(axis.text.y = element_blank(),
        legend.position = 'none',
        axis.ticks = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90),
        panel.background = element_rect(fill = 'gray70'),
        panel.grid.major.y = element_line(colour = "gray50",linetype = 3),
        panel.grid.major.x = element_line(colour = "gray50",linetype = 2),
        panel.grid.minor.x = element_line(colour = "gray50",linetype = 2),
        plot.background = element_rect(fill = 'gray70')) +
  labs(x = "",y = "Year") + 
  coord_flip()

dbClearResult(rs)
```

### ------------------------------------------------------------------------------------------------------------------

##### Stephen B Smith (Outlier in above graph

Firstly let us see what are different percentiles(25th,50th,75th and 90th) of all years played by these players.

```{sql,connection=connection}
SELECT PLAYER ,BEGIN,"END",PERCENTILE_25,"MEDIAN",PERCENTILE_75,PERCENTILE_95,"END" - BEGIN AS DAYS,("END" - BEGIN)/365 AS YEARS FROM
(SELECT PLAYER,MIN(MATCHDATE) BEGIN,MAX(MATCHDATE) "END",
PERCENTILE_CONT(0.25) WITHIN GROUP (ORDER BY MATCHDATE ASC) PERCENTILE_25 ,
PERCENTILE_CONT(0.5) WITHIN GROUP (ORDER BY MATCHDATE ASC) "MEDIAN",
PERCENTILE_CONT(0.75) WITHIN GROUP (ORDER BY MATCHDATE ASC) PERCENTILE_75 ,
PERCENTILE_CONT(0.95) WITHIN GROUP (ORDER BY MATCHDATE ASC) PERCENTILE_95 FROM ODI GROUP BY PLAYER)
ORDER BY YEARS DESC FETCH NEXT 10 ROWS ONLY
```

We see that almost 95% of matches played by **Stephen B Smith** are on or before *1985-02-04*.

```{r}
q = "SELECT TO_CHAR(MATCHDATE,'YYYY') STEPHEN_YEARS FROM ODI WHERE COUNTRY = 'Australia' AND PLAYER = 'Stephen B Smith'"
dbGetQuery(connection,statement = q) %>% table
```

I wonder whether **Stephen B Smith** played in ODI after 25 years (in 2011 since 1985)?
OR another player with same name entered in Australian team. This dataset doesen't have evidence for that.

#### Finally disconnecting from database
```{r}
dbDisconnect(connection)
```

### ------------------------------------------------------------------------------------------------------------------

[**REFERENCE : ** https://cran.r-project.org/web/packages/ROracle/ROracle.pdf](https://cran.r-project.org/web/packages/ROracle/ROracle.pdf)


###****************************************************************************************************